% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  12pt,
  letterpaper,
  man]{apa7}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{setspace}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother


% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}



\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 


\usepackage{csquotes}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={ReMis {[}A fun title could go here{]}},
  pdfauthor={Leonie Hagitte},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}


\title{ReMis {[}A fun title could go here{]}}
\author{Leonie Hagitte}
\date{}
\begin{document}
\maketitle


\setstretch{2}
\subsubsection{Introduction}\label{introduction}

Structural equation models (SEMs) are widely used in applied research to
test hypotheses about latent constructs and their relationships. In
practice, replication is typically assessed by fitting the same model to
a new dataset and evaluating whether global fit indices remain
acceptable or whether selected parameters retain statistical
significance. Empirically, these approaches often yield ambiguous or
unstable outcomes. Models may exhibit acceptable global fit across
datasets while differing substantially in parameter estimates,
reflecting the non-uniqueness of the model-implied covariance structure.
Conversely, parameters that were statistically significant in an
original study may fail to reach significance in a replication due to
differences in sample size, measurement quality, or sampling
variability. In addition, estimation itself may be unstable. A model
that converges in one dataset may fail to converge in another sample
drawn from the same population, or even in resampled versions of the
original data. Such behavior indicates sensitivity of the model to
sampling fluctuations or weak identification, and implies that
replication may fail at the level of model estimation rather than
parameter comparison. These issues highlight, that replication in SEM is
underdetermined and unsolved. To solve that problem, we argue that
replication of SEMs can be formalized as a problem of parameter
stability analogous to invariance testing.

\subsubsection{Replication}\label{replication}

Replication is the ability to obtain consistent findings when a study is
repeated with new independent data being collected under the same or
sufficiently similar methodological and theoretical conditions as the
original study. In the context of empirical research, a finding can be
understood at different analytical levels: as an empirical regularity,
as an estimand-based claim, or as a theoretical claim about an
underlying mechanism that generates observed patterns. The type or
extent of replication relevant to a finding depends on which of these
levels the finding is defined at.

Radder (1992) characterizes replication as comprising three distinct
forms: (a) material replication; (b) reproducibility of the theoretical
interpretation; and (c) replication of the experimental result through
an alternative material procedure. Schmidt (2009) builds on this
definition and establishes the concepts of direct replication as a
restrictive and narrow form of replication and conceptual replication as
a wider notion of replication.

Let \(d \in \{1,2\}\) index datasets, with \(d = 1\) denoting the
original study and \(d = 2\) the replication study. In direct
replication, the same estimand \(\theta^*\) is targeted under equivalent
conditions:

\[\theta^{*(1)} \approx \theta^{*(2)}. \]

Under finite sampling, exact equality,

\[\theta^{*(1)} =\theta^{*(2)}, \] is generally implausible.

Thus, direct replication refers to a repetition of the original
experimental or observational procedure aimed at re-estimating the same
estimand under equivalent conditions. This in turn relates to
non-experimental methods as when a new study estimates the same estimand
under conditions that are equal to the original, operationalizing the
variables in the same way, with differences limited to incidental
sources of variation such as sample, time, or setting. Under this
definition, deviations from exact numerical equality of coefficients are
to be minimal, however exact numerical equality is not neccessary.

By contrast, conceptual replication concerns the stability of a
theoretical claim under changes in operationalization. This relates to
Radder (1992), his b and c compartments of a replication, so that the
same theoretical claim or construct is supported using a different
estimand that is theoretically analogous to the original. This involves
changes in operationalization, such as different independent or
dependent measures, while retaining the underlying conceptual target.
Let \(\theta^{(1)} \in \Theta_1\) and \(\theta^{(2)} \in \Theta_2\)
denote estimands from two differently operationalized studies.
Conceptual replication can then be expressed through a mapping \(\phi\)
such that

\[C(\theta^{(1)}) = C(\phi(\theta^{(2)})), \]

where \(C(\cdot)\) denotes the theoretical claim supported by the
estimand. In this case, replication is evaluated at the level of
theoretical equivalence rather than parameter identity.

\subsubsection{Replicating Structural Equation
Models}\label{replicating-structural-equation-models}

According to Kaplan (2009), SEM comprises a class of methodologies
designed to express a hypothesized model through summary statistics
derived from empirical observations, parameterized by a reduced set of
structural parameters. As SEMs are also considered to be a way to
formulate social science theories(De Leeuw and Berk 2009), for a SEM to
be deemed replicated, the encompassed theory needs to hold in the data,
either globally or regarding certain parameters.

For models involving continuous latent variables, the associated
hypotheses typically pertain to the means, variances, and covariances of
the observed variables. Hypotheses may also concern effect sizes,
ordering of parameter magnitudes, or specific parameter values. Because
SEMs often contain many estimated parameters, replication should
generally focus on those outcomes that are substantively relevant to the
hypothesis under study.

\subsubsection{Global model fit versus parameter-level
replication}\label{global-model-fit-versus-parameter-level-replication}

Global model fit concerns the adequacy of the model-implied covariance
structure. Let \(\boldsymbol{\Sigma}(\theta)\) denote the covariance
matrix implied by the model parameters \(\theta\), and let
\(\mathbf{S}^{(d)}\) denote the observed covariance matrix in dataset
\(d\). Global fit evaluates whether

\[\boldsymbol{\Sigma}(\theta) \approx \mathbf{S}^{(d)}.\]

Equivalently, one may express this through a fitting function \(F\) such
that replication at the level of global fit would require

\[F\left(\mathbf{S}^{(d)}, \boldsymbol{\Sigma}(\hat{\theta}^{(d)})\right) \]

to be sufficiently small for both \(d = 1\) and \(d = 2\).

However, good global fit in both datasets does not imply replication at
the level of parameters. In general,

\[\boldsymbol{\Sigma}(\theta^{(1)}) \approx \boldsymbol{\Sigma}(\theta^{(2)})\]

does not imply

\[\theta^{(1)} \approx \theta^{(2)}. \]

Multiple parameter configurations may produce similar model-implied
covariance structures. Global fit therefore concerns the adequacy of the
model-implied distribution, whereas replication at the level of
parameters concerns the stability of theoretically relevant estimands.

Accordingly, let \(\theta^* \subset \theta\) denote the subset of
parameters that encode the substantive claim of interest. Replication at
the level of parameters is defined as

\[\theta^{*(1)} \approx \theta^{*(2)}. \]

This formulation captures replication as stability of theory-relevant
parameters, rather than mere admissibility of the overall model.

If i aim at replication it is therefore reasonable to treat both
datasets as independent realizations of the same underlying model. Thus,
it is a problem of symmetric parameter comparison across datasets. In a
multiple-group SEM framework, parameters are estimated freely in both
datasets and then compared through equality constraints imposed across
groups. This reflects the null hypothesis

\[ H_0: \theta^{*(1)} = \theta^{*(2)}, \]

which is formulated at the level of population parameters rather than
sample-specific estimates. Empirically, this hypothesis is assessed
using the corresponding parameter estimates. Because exact equality is
often too strict a criterion, approximate formulations are more
plausible, for example

\[\left|\hat\theta_j^{*(1)} - \hat\theta_j^{*(2)}\right| \le \epsilon_j \quad \forall j, \]

where \(\epsilon_j\) denotes a substantively justified tolerance for
parameter \(j\).

Under this perspective, replication of SEMs can be treated as analogous
to invariance testing across groups, with datasets taking the role of
groups. This analogy can be formalized using the framework of
measurement and structural invariance.

\subsubsection{Invariance Testing}\label{invariance-testing}

Measurement invariance (MI) refers to the statistical property that a
measurement instrument assesses the same latent construct equivalently
across different groups. In other words, the measurement model operates
in the same manner across groups. When MI is established, meaningful
comparisons of the underlying construct between groups are justified.

Let \(\mathbf{y}_i^{(g)}\) denote the observed variables for individual
\(i\) in group \(g\), and let \(\boldsymbol{\eta}_i^{(g)}\) denote the
corresponding latent variables. The measurement model can be written as

\[ 
\mathbf{y}_i^{(g)} = \boldsymbol{\nu}^{(g)} + \boldsymbol{\Lambda}^{(g)} \boldsymbol{\eta}_i^{(g)} + \boldsymbol{\varepsilon}_i^{(g)}, 
\] with

\[
\boldsymbol{\varepsilon}_i^{(g)} \sim (0, \boldsymbol{\Theta}^{(g)}).
\]

Where:

\begin{itemize}
\tightlist
\item
  \(\mathbf{y}_i^{(g)}\): observed responses of individual \(i\) in
  group \(g\)\\
\item
  \(\nu^{(g)}\): item intercepts\\
\item
  \(\eta_i^{(g)}\): latent variables for individual \(i\)\\
\item
  \(\Lambda^{(g)}\): factor loadings linking latent variables to
  observed indicators\\
\item
  \(\varepsilon_i^{(g)}\): residual errors
\item
  \(\Theta^{(g)}\): residual covariance matrix
\end{itemize}

From a statistical modelling perspective, MI refers to invariance of the
measurement parameters across groups:

\[ \theta_M^{(g)} = \theta_M \quad \forall g ,\]

where

\[ \theta_M = \{\boldsymbol{\Lambda}, \boldsymbol{\nu}, \boldsymbol{\Theta}\}. \]

\emph{Structural invariance} (SI), by contrast, refers to equality of
structural coefficients across groups, that is, to the requirement that
the same association between latent factors exists across groups. The
structural model may be written as

\[ \boldsymbol{\eta}_i^{(g)} = \boldsymbol{\alpha}^{(g)} + \mathbf{B}^{(g)} \boldsymbol{\eta}_i^{(g)} + \boldsymbol{\zeta}_i^{(g)}, \]

with

\[
\boldsymbol{\zeta}_i^{(g)} \sim (0, \boldsymbol{\Psi}^{(g)}).
\]

where

\begin{itemize}
\tightlist
\item
  \(\boldsymbol{\alpha}^{(g)}\) contains latent intercepts\\
\item
  \(\mathbf{B}^{(g)}\) contains the structural coefficients\\
\item
  \(\boldsymbol{\zeta}_i^{(g)}\) is a vector of structural disturbance
  terms\\
\item
  \(\boldsymbol{\Psi}^{(g)}\) is their covariance matrix
\end{itemize}

SI is then defined as

\[\theta_S^{(g)} = \theta_S \quad \forall g,\]

with

\[\theta_S = \{\mathbf{B}, \boldsymbol{\alpha}, \boldsymbol{\Psi}\}. \]

Traditionally, MI and SI are characterized via increasingly strict
levels of invariance that each add further restrictions on statistical
parameters across groups. In the classical view, MI is attained only
when configural, metric, scalar, and residual invariance hold. These
correspond to successive equality restrictions on
\(\boldsymbol{\Lambda}^{(g)}\), \(\boldsymbol{\nu}^{(g)}\), and
\(\boldsymbol{\Theta}^{(g)}\). More recent perspectives conceptualize
invariance as the absence of systematic moderation of key parameters by
variables external to the measurement model. Formally, if model
parameters depend on group membership through

\[ \theta^{(g)} = \theta + \Delta^{(g)}, \]

then invariance corresponds to the condition

\[ \Delta^{(g)} = 0 \quad \forall g. \]

Covariance invariance analyses evaluate whether the unstandardized
covariances among latent factors, represented by elements of
\(\boldsymbol{\Psi}^{(g)}\), are equivalent across groups, whereas SI
analyses examine whether the structural coefficients
\(\mathbf{B}^{(g)}\) are equal across groups. These analyses are
required to determine whether relationships between latent factors are
invariant across groups or vary systematically as a function of group
membership.

\subsubsection{Using Invariance Testing to replicate
SEMs}\label{using-invariance-testing-to-replicate-sems}

Where MI is conditional on group definitions, replication is conditional
on data independence. Formally,

\[\text{Replication} \Longleftrightarrow \theta^{*(d)} \text{ is stable across } d. \]

This definition is formulated at the level of population parameters.
Empirically, stability is assessed using the corresponding sample-based
parameter estimates \(\hat{\theta}^{*(d)}\). This makes the relation to
MI and SI explicit: both invariance testing and replication evaluate
robustness of parameters under variation, differing mainly in the source
of that variation. Replication of SEMs across an original and a
replication sample should therefore proceed within a sequential
multiple-group manner. First, measurement invariance between the two
samples has to be established:

\[\theta_M^{(1)} = \theta_M^{(2)}. \]

At least metric invariance is required for structural parameters to be
meaningfully compared, because without comparable factor loadings,
differences in structural relations may reflect measurement
non-equivalence rather than substantive divergence. Conditional on
sufficient measurement invariance, structural replication is assessed by
comparing an unconstrained multiple-group model, in which the structural
parameters of interest are freely estimated across datasets, with a
constrained model in which they are set to be equal:

\[ H_0: \theta_S^{*(1)} = \theta_S^{*(2)}. \]

This comparison could be evaluated with a likelihood-ratio statistic,

\[ \Delta \chi^2 = -2(\ell_C - \ell_U), \]

where \(\ell_C\) and \(\ell_U\) denote the log-likelihoods of the
constrained and unconstrained models, respectively. If a model in which
the parameters are constrained to be equal across groups fits the data
no worse than a model in which they are freely estimated, this is
consistent with structural stability of those parameters. Conversely, if
the constrained model fits the data worse, this indicates that the
parameters differ across groups. At the same time, such tests should be
interpreted cautiously because they are sensitive to sample size and do
not by themselves capture uncertainty in a substantively calibrated way.

At the level of parameters, again some would consider SEMs replicated
when the statistical significance of paths and correlations is
consistent across studies. However, failure to reproduce statistical
significance does not necessarily imply non-replication, because
significance is highly sensitive to sampling variability, statistical
power, and measurement error. Replication should therefore not be
reduced to consistency of significance decisions alone. This implies
that replication of SEMs is best understood as a graded, parameter- and
claim-relative process.\\
Let

\[ \theta^* = \{\theta_1^*, \dots, \theta_r^*\} \]

denote the set of parameters relevant to the theoretical claim of
interest. Replication can then be represented as the vector

\[ \hat{R} = \left( \mathbb{I}\left(\left|\hat\theta_j^{*(1)} - \hat\theta_j^{*(2)}\right| \le \epsilon_j\right) \right)_{j=1}^r, \]

where \(\mathbb{I}(\cdot)\) is an indicator function and \(\epsilon_j\)
is a substantively justified tolerance for parameter \(j\). A parameter
is said to be empirically \emph{stable} if

\[\left|\hat\theta_j^{*(1)} - \hat\theta_j^{*(2)}\right| \le \epsilon_j.\]

Full replication corresponds to the case in which all relevant
parameters satisfy this condition, whereas partial replication
corresponds to stability of only a subset of them.

This perspective renders approximate and partial replication
theoretically grounded rather than ad hoc. Limited deviations in
parameter estimates can then be interpreted as meaningful quantitative
differences rather than categorical failures of replication, paralleling
contemporary approaches to approximate invariance. It follows that
models in their entirety should not be treated as the primary objects of
replication. Rather, models serve as entry points for evaluating the
stability of the theoretical commitments they encode. This shifts
attention away from global model fit toward the robustness of
substantively meaningful parameters. In this sense, global fit is a
necessary but not sufficient condition for replication:

\[ \text{Replication} \Rightarrow \text{adequate model fit}, \]

but the converse does not hold. Measurement quality also becomes central
to replication validity, because instability across datasets may reflect
violations of

\[ \theta_M^{(1)} = \theta_M^{(2)} \]

rather than instability of structural relations. Replication claims that
do not explicitly address measurement equivalence therefore remain
ambiguous.

Conceptual replication has a formal structure under this perspective as
it concerns stability of higher-level theoretical claims under
deliberate changes in operationalization. This can be understood as
stability of \(C(\cdot)\) under transformations of the estimand space,
rather than equality of the same parameter across datasets. Replication
success therefore becomes explicitly conditional on the estimand, the
theoretical scope, and the operational context, requiring precise
statements about what exactly has or has not replicated. The distinction
between invariance testing and replication may therefore be understood
as one of scope rather than kind. Invariance evaluates stability across
groups within a dataset, whereas replication evaluates stability across
independent datasets or study instantiations, but both address the same
underlying question of robustness under variation.

\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-DeLeeuw2009}
De Leeuw, J., and R. Berk. 2009. {``{Preface}.''} In \emph{Structural
Equation Modeling: Foundations and Extensions}, edited by J. De Leeuw
and R. Berk, 2nd ed., vi. SAGE Publications, Inc.
\url{https://doi.org/10.4135/9781452226576}.

\bibitem[\citeproctext]{ref-Kaplan2009}
Kaplan, David. 2009. \emph{Structural {Equation} {Modeling} (2nd Ed.):
{Foundations} and {Extensions}}. Edited by J. De Leeuw and R. Berk. 2nd
ed. Thousand Oaks, California: SAGE Publications, Inc.
\url{https://doi.org/10.4135/9781452226576}.

\bibitem[\citeproctext]{ref-Radder1992}
Radder, Hans. 1992. {``Experimental Reproducibility and the
Experimenters' Regress.''} \emph{PSA: Proceedings of the Biennial
Meeting of the Philosophy of Science Association} 1992: 63--73.
\url{http://www.jstor.org/stable/192744}.

\bibitem[\citeproctext]{ref-Schmidt2009}
Schmidt, Stefan. 2009. {``Shall We {Really} Do It {Again}? {The}
{Powerful} {Concept} of {Replication} Is {Neglected} in the {Social}
{Sciences}.''} \emph{Review of General Psychology} 13 (2): 90--100.
\url{https://doi.org/10.1037/a0015108}.

\end{CSLReferences}




\end{document}
